### 2016-03-14 paper/layered_depthmap.tex

Our last problem is layered depthmap estimation, recently proposed
in~\cite{layered_depthmap} (see the anonymous paper in the
supplementary material).  The problem seeks to infer layered depthmap
representation from an RGBD image, where each layer is a piecewise
smooth segmented depthmap. This is essentially a multi-layer extension
of Surface Stereo algorithm~\cite{surface_stereo}.
%
Layered depthmap estimation is a very challenging MRF inference problem
due to its massive solution space. The number of labels per pixel is
exponential in the number of layers, and is usually between 100,000 and
10,000,000. We copy their problem formulation and the proposal
generation schemes.~\footnote{Authors have proposed a novel fusion
scheme, where a solution subspace instead of a single solution is
generated by a proposal generation scheme. Since a solution subspace can
be represented by a concatenation of multiple solution proposals,
% \chen{It is a good explanation for this paper's purpose, but from the perspective of our previous work, I am reluctant to say a subspace equals to multiple solution proposals. When we design proposals, we find the subspace directly and there's no concept of solution proposals (we later simplify our subspace proposals to binary labels just for the comparison reason). It is essentially the same, but a subspace proposal is conceptually more general than concatenated solution proposals.},
their algorithm can be easily integrated into our swarm fusion framework.
However, competing fusion methods (e.g., Parallel Fusion Move or
Hierarchical Fusion) cannot handle a solution subspace proposal, making
it impossible to conduct fair comparative evaluations. We choose to use
a simple solution proposal for this experiment.}
%Lastly, we will evaluate Swarm fusion on a very challenging layered
%depthmap estimation problem~\cite{layered_depthmap}, which has been
%recently proposed (see the anonymized pdf in the supplementary
%material).

@@

\noindent Solution proposals depend heavily on the current solution,
eliminating the possibility of using Hierarchical Fusion, which needs to
enumerate all the proposals to start. Therefore, viable competing
methods are Fusion Move and Parallel Fusion Move.
%
%We will also evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

@@

\mysubsubsection{Swarm fusion architectures}

\noindent The three swarm architectures with the same configurations as
in the optical flow problems have been evaluated.
%in Fig.~\ref{fig:model} are evaluated.
%The architecture parameters are exactly the same as in the optical flow problem:
%$\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
%($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
%($\alpha=1, \beta=1$) for the standard SF.
%
%The fusions are multi-way, for which we use TRW-S.

>>>>

Our last problem is layered depthmap estimation, recently proposed
in~\cite{layered_depthmap} (see the anonymous paper in the
supplementary material).  The problem seeks to infer layered depthmap
representation from an RGBD image, where each layer is a piecewise
smooth segmented depthmap. This is essentially a multi-layer extension
of Surface Stereo algorithm~\cite{surface_stereo}.
%
Layered depthmap estimation is a very challenging MRF inference problem
due to its massive solution space. The number of labels per pixel is
exponential in the number of layers, and is usually between 100,000 and
10,000,000. We copy their problem formulation and the proposal
generation schemes.~\footnote{Authors have proposed a novel fusion
scheme, where a solution subspace instead of a single solution is
generated by a proposal generation scheme. Since a solution subspace can
be represented by a concatenation of multiple solution proposals,
% \chen{It is a good explanation for this paper's purpose, but from the perspective of our previous work, I am reluctant to say a subspace equals to multiple solution proposals. When we design proposals, we find the subspace directly and there's no concept of solution proposals (we later simplify our subspace proposals to binary labels just for the comparison reason). It is essentially the same, but a subspace proposal is conceptually more general than concatenated solution proposals.},
their algorithm can be easily integrated into our Swarm Fusion framework.
However, competing fusion methods (e.g., Parallel Fusion Move or
Hierarchical Fusion) cannot handle a solution subspace proposal, making
it impossible to conduct fair comparative evaluations. We choose to use
a simple solution proposal for this experiment.}
%Lastly, we will evaluate Swarm fusion on a very challenging layered
%depthmap estimation problem~\cite{layered_depthmap}, which has been
%recently proposed (see the anonymized pdf in the supplementary
%material).

@@

\noindent In this problem setting, solution proposals depend heavily on the current solution,
eliminating the possibility of using Hierarchical Fusion Move (HFM), which needs to
enumerate all the proposals to start. Therefore, viable competing
methods are Fusion Move (FM) and Parallel Fusion Move (PFM) as in the optical flow problem.
%
%We will also evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

@@

\mysubsubsection{Swarm Fusion architectures}

\noindent The three swarm architectures with the same configurations as
in the optical flow problem have been evaluated.
%in Fig.~\ref{fig:model} are evaluated.
%The architecture parameters are exactly the same as in the optical flow problem:
%$\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
%($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
%($\alpha=1, \beta=1$) for the standard SF.
%
%The fusions are multi-way, for which we use TRW-S.

### 2016-03-14 paper/result_stereo.tex
Hang

Fig.~\ref{fig:stereo_global} compares the converegence rate of the
competing methods. Note that we define the energy of a multi-threading
system to be the energy of the best solution found so far.
%
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
 \caption{Energy plots for the stereo problem. The energy is in the log
 scale. For a multi-threading algorithm, the energy at a given moment is
 defined to be the best solution so far.} \label{fig:stereo_global}
\end{figure}
%
One unusual outcome is that Sequential Alpha Expansion and Parallel
Alpha Expansion (PAE) have the same convergence speed, indicating that
the stereo problem is a very easy one.
%This is well known in a community and this fact was rather expected.
Our approaches with multi-way fusion (SF-SS or SF) are the slowest kind,
because the TRW-S for multi-way fusion is slower than multiple Alpha
Expansion steps, and this stereo problem is too easy to gain benefits
through mulit-way fusion.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Fig. \ref{fig:stereo_threads} shows the energy plot per thread
for SF-MF (ours) and PAE. The graph for PAE again confirms that the
stereo is an easy problem, because all the threads are quickly
converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{Energy plots per thread for the stereo proble for SF-MF (left) and
 Parallel Alpha Expansion (right).
} \label{fig:stereo_threads}
\end{figure}

>>>>

Fig.~\ref{fig:stereo_global} compares the converegence rate of the
competing methods. Note that we define the energy of a multi-threading
system to be the energy of the best solution found so far.
%

\begin{figure}[tb]
\centering
\includegraphics[width=0.8\textwidth]{figure/stereo_global.png}
\caption{Energy plots for the stereo problem. The energy is in the log
scale. For a multi-threading algorithm, the energy at a given moment is
defined to be the best solution so far.}
\label{fig:stereo_global}
\end{figure}
%

One unusual outcome is that Sequential Alpha Expansion and Parallel
Alpha Expansion (PAE) have the same convergence speed, indicating that
the stereo problem is a very easy one.
%This is well known in a community and this fact was rather expected.
Our approaches with multi-way fusion (SF-SS or SF) are the slowest kind,
because the TRW-S for multi-way fusion is slower than multiple Alpha
Expansion steps, and this stereo problem is too easy to gain benefits
through mulit-way fusion.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Fig. \ref{fig:stereo_threads} shows the energy plot per thread
for SF-MF (ours) and PAE. The graph for PAE again confirms that the
stereo is an easy problem, because all the threads are quickly
converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.

%% \begin{figure}[tb]
%% \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
%% \caption{Energy plots per thread for the stereo proble for SF-MF (left) and
%% Parallel Alpha Expansion (right).
%% } \label{fig:stereo_threads}
%% \end{figure}
